% universal settings
\documentclass[smalldemyvopaper,11pt,twoside,onecolumn,openany,extrafontsizes]{memoir}

% note: i just copy/pasted this .tex file from a different danmei
% typesetting project, so there's a lot of preamble cruft that
% isn't really relevant to this project.

% PACKAGE DEFINITION
% typographical packages
\usepackage{microtype} % for micro-typographical adjustments
\usepackage{setspace} % for line spacing
\usepackage{lettrine} % for drop caps and awesome chapter beginnings
\usepackage{titlesec} % for manipulation of chapter titles

\usepackage{type1cm}
\usepackage{titling}
\usepackage{fontspec}
\usepackage{newunicodechar}
\usepackage{tocloft}
\usepackage{ragged2e}
\usepackage[UTF8]{ctex}
\usepackage{xeCJK}
\usepackage{etoolbox}
\usepackage{environ}
\usepackage{needspace}

\setmainfont{Baskerville}[
  SmallCapsFont={Baskerville Small Caps SSi},
  SmallCapsFeatures={Letters=SmallCaps},
]
\setCJKmonofont{Noto Sans SC Light}
\setCJKsansfont{Noto Sans SC Light}
\setmonofont{Noto Sans Mono}
\newfontfamily{\dropcaps}{Zallman Caps}

\def\CJKmovesymbol#1{\lower0.15em\hbox{#1}}
\def\CJKmove{\let\CJKsymbol\CJKmovesymbol
             \let\CJKpunctsymbol\CJKmovesymbol}

\newcommand{\nicecjk}[1]{\textsf{\CJKmove{#1}}}

\makeatletter                                                                   
\newcommand\pinyin[1]{\begingroup \language=\l@pinyin #1\endgroup}              
\makeatother

\usepackage{url}
\usepackage{relsize}

% other
\usepackage{calc}
\usepackage{hologo}
\usepackage[hidelinks]{hyperref}
%\usepackage{showframe}
\usepackage{sepfootnotes}
\usepackage{amssymb}

% PHYSICAL DOCUMENT SETUP
% media settings
\setstocksize{5.675in}{4.375in}
\settrimmedsize{5.5in}{4.25in}{*}
\setbinding{0.175in}
\setlrmarginsandblock{0.5in}{0.5in}{*}
\setulmarginsandblock{0.6in}{0.6in}{*}

% defining the title and the author
\title{My First Sixteen Days as a Second Century Warlord}
\author{tumblr user romanceyourdemons}
\newcommand{\press}{Alpaca Laboratories Press}

% custom second title page
\makeatletter
\newcommand*\halftitlepage{\begingroup % Misericords, T&H p 153
  \setlength\drop{0.1\textheight}
  \begin{center}
  \vspace*{\drop}
  \rule{\textwidth}{0in}\par
  {\Large\thetitle\par}
  \rule{\textwidth}{0in}\par
  \vfill
  \end{center}
\endgroup}
\makeatother

% custom title page
\thispagestyle{empty}
\makeatletter
\newlength\drop
\newcommand*\titleM{\begingroup % Misericords, T&H p 153
  \setlength\drop{0.15\textheight}
  \begin{center}
  \vspace*{\drop}
  \rule{\textwidth}{0in}\par
  {\HUGE\thetitle\par}
  \rule{\textwidth}{0in}\par
  {\Large\textit\theauthor\par}
  \vfill
  {\Large\scshape\press}
  \end{center}
\endgroup}
\makeatother

\renewcommand*\thechapter{\ifnum\value{chapter}<10 0\fi\arabic{chapter}}

\chapterstyle{dash}
\setlength{\beforechapskip}{0\onelineskip}
\setlength{\afterchapskip}{2\onelineskip}

\newcommand{\dotbreak}{%
  \fancybreak{$\cdot$ $\cdot$ $\cdot$}%
}

% typographical settings for the body text
\linespread{1.09}

% HEADER AND FOOTER MANIPULATION
  % for normal pages
  \nouppercaseheads
  \headsep = 0.4in
  \makepagestyle{mystyle} 
  \setlength{\headwidth}{\dimexpr\textwidth+\marginparsep+\marginparwidth\relax}
  \makerunningwidth{mystyle}{\headwidth}
  \makeevenhead{mystyle}{}{}{}
  \makeoddhead{mystyle}{}{}{}
  \makeevenfoot{mystyle}{}{\textsf{\scriptsize\scshape\thepage}}{}
  \makeoddfoot{mystyle}{}{\textsf{\scriptsize\scshape\thepage}}{}
  %\makeevenhead{mystyle}{}{\textsf{\scriptsize\scshape\thetitle}}{}
  %\makeoddhead{mystyle}{}{\textsf{\scriptsize\scshape\leftmark}}{}
  %\makeevenfoot{mystyle}{}{\textsf{\scriptsize\scshape\thepage}}{}
  %\makeoddfoot{mystyle}{}{\textsf{\scriptsize\scshape\thepage}}{}
  \makeatletter
  \makepsmarks{mystyle}{%
  \createmark{chapter}{left}{nonumber}{\@chapapp\ }{.\ }}
  \makeatother
  % for pages where chapters begin
  \makepagestyle{plain}
  \makerunningwidth{plain}{\headwidth}
  \makeevenfoot{plain}{}{\textsf{\scriptsize\scshape\thepage}}{}
  \makeoddfoot{plain}{}{\textsf{\scriptsize\scshape\thepage}}{}
  \pagestyle{mystyle}
% END HEADER AND FOOTER MANIPULATION

% table of contents customisation
\renewcommand\contentsname{\normalfont\scshape Contents}
\renewcommand\cftchapterfont{\normalfont}
\renewcommand{\cftchapterpagefont}{\normalfont}
\renewcommand{\printtoctitle}{\centering\Huge}

\newlength{\mylen}   % a "scratch" length
\setlength{\mylen}{0.5em}   % need some extra space at end of number
\settowidth{\mylen}{\bfseries\cftchapterpresnum\cftchapteraftersnum} % extra space
\addtolength{\cftchapternumwidth}{1.2em} % add the extra space
\renewcommand{\cftchapteraftersnum}{\, $\cdot$}

\emergencystretch 3em
\hfuzz .5pt

% layout check and fix
\checkandfixthelayout
\fixpdflayout

\renewcommand*{\UrlFont}{\ttfamily\smaller\relax}

\renewcommand{\precisfont}{\small\normalfont\itshape}
\renewenvironment{quote}%
  {\list{}{\leftmargin=0.4in\rightmargin=-0.4in}\item[]}%
  {\endlist}
\AtBeginEnvironment{quote}{\itshape}

\newsavebox{\saveblock}
\NewEnviron{newpageblock}{%
  \par
  \addvspace{.5\baselineskip}%
  \begin{lrbox}{\saveblock}
    \begin{minipage}{\linewidth}
      \BODY
    \end{minipage}
  \end{lrbox}%
  \Needspace{\dimexpr\ht\saveblock+\dp\saveblock}%
  \BODY
}

\newsavebox{\ansaveblock}
\NewEnviron{authornote}{
  \vspace{10pt}%
  \begin{lrbox}{\ansaveblock}
  \begin{minipage}{\linewidth-1.0in}
  \BODY
  \end{minipage}
  \end{lrbox}%
  \Needspace{\dimexpr\ht\ansaveblock+\dp\ansaveblock}%

  \noindent \hspace{0.2in}
  \textit{The author has something to say ---}
  \vspace{-8pt}
  \def\FrameCommand{
    \hspace{0.4in}
    {\vrule width 0.5pt}
    \hspace{2pt}
  }
  \MakeFramed{\advance\hsize-\width\FrameRestore}
  \begin{adjustwidth}{5pt}{5pt}
  \vspace{-2pt}
  \BODY
  \vspace{2pt}
  \end{adjustwidth}
  \endMakeFramed
}

\newsavebox{\tlsaveblock}
\NewEnviron{tlnote}{
  \begin{lrbox}{\tlsaveblock}
  \begin{minipage}{\linewidth-1.0in}
  \BODY
  \end{minipage}
  \end{lrbox}%
  \Needspace{\dimexpr\ht\tlsaveblock+\dp\tlsaveblock}%

  \noindent \hspace{0.2in}
  \textit{Translator's note ---}
  \vspace{-10pt}
  \def\FrameCommand{
    \hspace{0.4in}
    {\vrule width 0.5pt}
    \hspace{2pt}
  }
  \MakeFramed{\advance\hsize-\width\FrameRestore}
  \begin{adjustwidth}{5pt}{5pt}
  \vspace{-2pt}
  \BODY
  \vspace{2pt}
  \end{adjustwidth}
  \endMakeFramed
}
\AtBeginEnvironment{tlnote}{\itshape}

\newsavebox{\edsaveblock}
\NewEnviron{ednote}{
  \begin{lrbox}{\edsaveblock}
  \begin{minipage}{\linewidth-1.0in}
  \BODY
  \end{minipage}
  \end{lrbox}%
  \Needspace{\dimexpr\ht\edsaveblock+\dp\edsaveblock}%

  \noindent \hspace{0.2in}
  \textit{Editor's note ---}
  \vspace{-10pt}
  \def\FrameCommand{
    \hspace{0.4in}
    {\vrule width 0.5pt}
    \hspace{2pt}
  }
  \MakeFramed{\advance\hsize-\width\FrameRestore}
  \begin{adjustwidth}{5pt}{5pt}
  \vspace{-2pt}
  \BODY
  \vspace{2pt}
  \end{adjustwidth}
  \endMakeFramed
}
\AtBeginEnvironment{ednote}{\itshape}


% BEGIN THE DOCUMENT
\begin{document}
\pagestyle{empty}
% the half title page
\halftitlepage
\cleardoublepage
% the title page
\titleM
\clearpage
% copyright page
\begin{center}
\vfill
Published by \press, 2023
\end{center}

\medskip

Originally published on tumblr.com at \\
\url{romanceyourdemons.tumblr.com/post/706591865612451840}

\vfill
\clearpage

% begin front matter
\frontmatter
\pagestyle{mystyle}
\tableofcontents*
\mainmatter

\chapter{first day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, have my men} tie branches to their
horses' tails to stir up dust and make it look like there's a lot of us but i
forget it just rained so there isn't any dust and the enemy can clearly see
there's like twenty of us all spread out in a line

\chapter{second day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, bribe a bunch} of kids to start
singing a nursery rhyme i carefully crafted to spread misinformation and further
my strategic ends but they change the lyrics to be about poop and the enemy
isn't misdirected at all

\chapter{third day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, lure my enemy} into a narrow
valley and send a team of archers to shoot them from the high ground but there
was a feral hog napping on the trail up to the overlook and they couldn't
decide whether to try and shoot it or just go around and by the time the hog
woke up and left on its own the enemy had already passed safely below

\chapter{fourth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,slope=-3pt,findent=-2pt]{\dropcaps{w}}{e attempt to} join a battle on
the side of the guy we want to ally with but he and the guy he's fighting
have really similar names and it's finally dusty and i misread the standards
and attack the wrong guy.  so now we're stuck with this total loser of a
liege lord, because how the fuck do you explain that after a battle?

\chapter{fifth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=0pt]{\dropcaps{a}}{nd some sort}
of wizard wanders into camp, my loser liege lord wants to execute him for
being a wizard but i convince him to let the wizard stay, because i want
to do more weather-based strategies and i'm pretty sure having a camp
wizard can help with that.  after the welcome to the team banquet the wizard
steals half the treasury and my liege lord's wife and leaves

\chapter{sixth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=-2pt]{\dropcaps{m}}{y loser liege lord}
sends me to reinforce a city he's taken, but in the confusion of leaving i
forgot to take the token that would have gotten us into the city, so my men
have to wait outside the city walls for like eight hours while i ride
back to get it

\chapter{seventh day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=0pt]{\dropcaps{a}}{nd my loser} liege lord
finally joins me in the city, it turns out he's actually a pretty cool guy, and
he isn't even that mad at me for letting the wizard steal his wife. i decide to
shoot my shot but i'm really nervous and keep on stalling because what if i
mess up our relationship and by extension jeopardize the security of my men,
and eventually he just says goodnight and goes back to his room, where an
assassin is in the process of setting up to kill him

\chapter{eighth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=0pt]{\dropcaps{a}}{nd my loser} liege lord
tells me to fake defect to his rival warlord, the one i originally wanted to
ally with, to find out if he was the one who sent the assassin and why.
but my whole way over to the rival warlord i'm worried that this has something
to do with the wizard thing or how awkward i made it last night 

\chapter{ninth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, try to tactfully}
ask my fake liege lord if he sent the assassin to kill my loser liege lord and
it turns out the idea of using assassins never occurred to him, but now that
i've suggested it he's really into it. in order to save my loser liege lord i
volunteer to be the one to kill him

\chapter{tenth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{o}}{n my way back} to my
loser liege lord's city i realize i won't be able to collect my men from my
fake liege lord until i bring back my loser liege lord's head. this would have
been a great thing to think of before i got myself in this situation. i go back
to my loser liege lord and ask him to rescue my men, and he tells me that if he
could sack my fake liege lord's camp he already would have. that doesn't change
the fact that my men are still trapped. they're prisoners, even. i go back to
my room to sulk

\chapter{eleventh day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, find a little}
caged pigeon in the rafters of my loser liege lord's room and deduce it
belonged to the assassin. without asking permission or telling my loser liege
lord goodbye i let the pigeon loose and follow it north. don't ask what i was
doing in my loser liege lord's room. it's not important

\chapter{twelfth day\\as a second century warlord}

\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, disguise myself}
as a wizard and enter the camp of the coalition leader the pigeon led me to.
in the middle of my little sleight of hand performance i make eye contact with
the coalition leader's second-in-command. IT'S THE WIZARD THAT STOLE MY LOSER
LIEGE LORD'S WIFE. after the banquet i corner the fake wizard and ask him what
the fuck is going on and he just says ``wouldn't you like to know'' and leaves.
i don't know what to say to that so i just let him go

\chapter{thirteenth day\\as a second century warlord}
\lettrine[lhang=0.2,lines=3,findent=0pt]{\dropcaps{I}}{'m honestly so} sick of
not knowing what's going on, so i adjust my wizard costume to passably disguise
myself as a woman and break into the women's area of the camp, where sure
enough my loser liege lord's wife is. i ask her what she's doing here and she
tells me the fake wizard overheard her singing a poem she overheard on the
street, not knowing it contains the coalition leader's formation's weaknesses.
the fake wizard kidnapped her and assigned an assassin to kill her husband
before they figured out the poem's significance. she shares the first couplet
with me but i'm discovered and thrown out before she can share any more.
she doesn't need to. through a bizarre coincidence of homophones, it's the
poop version of my misinformation nursery rhyme

\chapter{fourteenth day\\as a second century warlord}
\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{I}}{\, go back to}
my loser liege lord and tell him everything, urging him to join with my fake
liege lord to attack the coalition leader according to the weaknesses in the
nursery rhyme. he tells me frankly that he doesn't trust me anymore. i ask him
to execute me if that's really true, because i can't bear to live if i can't
protect him and i can't protect my men. he agrees to attack the coalition leader

\chapter{fifteenth day\\as a second century warlord}
\lettrine[lhang=0.2,lines=3,findent=2pt]{\dropcaps{d}}{ue to the} information
in the nursery rhyme, and thanks to my loser liege lord reminding me of the
weather conditions multiple times while planning our battle strategy, our
alliance carries the day. my loser liege lord gets his wife back. my men tell
me that our fake liege lord actually treated them really well and they'd like
to stay with him if i don't mind. i do mind, now that neither the men i love
nor the man i love have any use for me, but i don't tell them that

\chapter{sixteenth day\\as a second century warlord}
\lettrine[lhang=0.2,lines=3,findent=0pt]{\dropcaps{I}}{'m preparing to}
leave to i don't know where, maybe to try to become a wizard for real, when my
loser liege lord stops me and asks me where i'm going. he says he had hoped i
would continue to work as his advisor. i was unaware i was his advisor in the
first place. i agree, and he tells me he's truly honored to have me in his
service at last. he has known i am a rare and talented man with a strategic
intelligence far above his ever since the day he witnessed me tying branches to
my horses' tails in six inches of mud, and could not for the life of him figure out why

\end{document}
